\chapter*{Références Bibliographiques}
\addcontentsline{toc}{chapter}{Références Bibliographiques}
\markboth{Références Bibliographiques}{Références Bibliographiques}

\begin{enumerate}[label={[\arabic*]}, leftmargin=1.5cm, itemsep=5pt]

  \item Bellman, R.\,E. (1961). \textit{Adaptive Control Processes: A Guided Tour}. Princeton University Press.

  \item Breiman, L. (2001). Random forests. \textit{Machine Learning}, 45(1), 5--32.

  \item Chen, T., \& Guestrin, C. (2016). XGBoost~: A scalable tree boosting system. \textit{Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, 785--794.

  \item Géron, A. (2022). \textit{Hands-On Machine Learning with Scikit-Learn, Keras, and TensorFlow} (3\textsuperscript{e} éd.). O'Reilly Media.

  \item Goodfellow, I., Bengio, Y., \& Courville, A. (2016). \textit{Deep Learning}. MIT Press.

  \item Han, J., Pei, J., \& Tong, H. (2022). \textit{Data Mining: Concepts and Techniques} (4\textsuperscript{e} éd.). Morgan Kaufmann.

  \item Lundberg, S.\,M., \& Lee, S.-I. (2017). A unified approach to interpreting model predictions. \textit{Advances in Neural Information Processing Systems}, 30.

  \item Provost, F., \& Fawcett, T. (2013). \textit{Data Science for Business}. O'Reilly Media.

  \item Rubin, D.\,B. (1976). Inference and missing data. \textit{Biometrika}, 63(3), 581--592.

  \item Shi, W., Cao, J., Zhang, Q., Li, Y., \& Xu, L. (2016). Edge computing~: Vision and challenges. \textit{IEEE Internet of Things Journal}, 3(5), 637--646.

  \item Vapnik, V. (1995). \textit{The Nature of Statistical Learning Theory}. Springer.

  \item Wirth, R., \& Hipp, J. (2000). CRISP-DM~: Towards a standard process model for data mining. \textit{Proceedings of the 4th International Conference on the Practical Application of Knowledge Discovery}, 1--13.

  \item FAO (2023). \textit{FAOSTAT --- Food and Agriculture Data}. Organisation des Nations Unies pour l'Alimentation et l'Agriculture. Disponible sur~: \url{https://www.fao.org/faostat}

  \item Kaggle Dataset (2023). \textit{Crop Yield Prediction Dataset}. Disponible sur~: \url{https://www.kaggle.com/datasets/patelris/crop-yield-prediction-dataset}

  \item Pedregosa, F. et al. (2011). Scikit-learn: Machine learning in Python. \textit{Journal of Machine Learning Research}, 12, 2825--2830.

\end{enumerate}

\newpage
